---
title: "Exp 1"
output:
  pdf_document: default
  html_document:
    df_print: paged
header-includes:
 \usepackage{booktabs}
 \usepackage{longtable}
 \usepackage{array}
 \usepackage{multirow}
 \usepackage{wrapfig}
 \usepackage{float}
 \floatplacement{figure}{H}
---

# Setup

```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H', 
                      echo=TRUE, warning=FALSE, message=FALSE)

```
```{r , include=FALSE}
library(tidyverse)
library(estimatr)
library(hexbin)
library(ggplot2)
library(readr)
library(stargazer)


th <- theme_minimal()
theme_set(th)
```

## Load Data

```{r echo=TRUE, results='hide'}
subject_data <- read_csv("data/parsed_trials.csv") %>%
  select(-c(WID)) %>%
  replace_na(list(response_frame = Inf))

structure_data <- read_csv("data/exp3_polygons_structure.csv")
```

Plot structure against TD acc

```{r}
td_by_subj_tracker <- subject_data %>%
  pivot_longer(cols = starts_with("td"), 
               names_to = "tracker", 
               values_to = "td") %>%
  separate(tracker, c("NA", "tracker")) %>%
  mutate(tracker = as.numeric(tracker)) %>%
  group_by(ID, scene, tracker) %>%
  summarise(td = first(td)) 

td_by_scene <- td_by_subj_tracker %>%
  group_by(scene) %>%
  summarise(td = mean(td))

td_by_subj_scene <- td_by_subj_tracker %>%
  group_by(ID, scene) %>%
  summarise(td = mean(td))

td_by_subj <- td_by_subj_tracker %>%
  group_by(ID) %>%
  summarise(td_acc_mu = mean(td),
            n = n(),
            td_acc_se = sd(td) / sqrt(n)) 

```


```{r}
td_by_scene %>%
  left_join(structure_data) %>%
  ggplot() +
  geom_point(aes(x=td, y=rel_structure))
  

```



```{r}
hr_by_subj_scene <- with_probes %>%
  group_by(ID, scene, probe) %>%
  summarise(hit = any(hit)) %>%
  group_by(ID, scene) %>%
  summarise(hr = mean(hit))

fp_by_subj_scene <- with_probes %>%
  group_by(ID, scene, response_frame) %>%
  summarise(fp = any(fp)) %>%
  group_by(ID, scene) %>%
  summarise(fpr = mean(fp))

probe_by_subj <- hr_by_subj_scene %>%
  left_join(fp_by_subj_scene) %>%
  group_by(ID) %>%
  summarise(hr = mean(hr),
            fp = mean(fpr))

td_by_subj_tracker <- subject_data %>%
  pivot_longer(cols = starts_with("td"), 
               names_to = "tracker", 
               values_to = "td") %>%
  separate(tracker, c("NA", "tracker")) %>%
  mutate(tracker = as.numeric(tracker)) %>%
  group_by(ID, scene, tracker) %>%
  summarise(td = first(td)) 

td_by_subj_scene <- td_by_subj_tracker %>%
  group_by(ID, scene) %>%
  summarise(td = mean(td))

td_by_subj <- td_by_subj_tracker %>%
  group_by(ID) %>%
  summarise(td_acc_mu = mean(td),
            n = n(),
            td_acc_se = sd(td) / sqrt(n)) 

perf_thresh = 3.0
subject_performance <- td_by_subj %>%
  left_join(probe_by_subj) %>%
  mutate(passed = (td_acc_mu - 0.5) > perf_thresh*td_acc_se & hr > 0)

good_subjects_data <- subject_performance %>%
  filter(passed) %>%
  select(ID) %>%
  left_join(with_probes, by = "ID") %>%
  left_join(hr_by_subj_scene) %>%
  left_join(td_by_subj_scene, by = c("ID", "scene")) %>%
  ungroup()

# %>%
#   filter(td == 1)


```

# Analysis



## Causal effects

First collect all data points (no averaging across scene)

The the average treatment effect, ATE, is indentified over attention on probe detection
regardless of target designation accuracy.

The condititional average treatement effect, CATE, is the ATE conditioned on
correct (4/4) target designation.


```{r}
hr_by_probe <- good_subjects_data %>%
  # sorting out probed tracker
  pivot_longer(cols = starts_with("probe_"), 
               names_to = "probed_tracker_epoch",
               values_to = "tracker") %>%
  separate(probed_tracker_epoch, c(NA, NA, "probed_tracker_epoch")) %>%
  mutate(probed_tracker_epoch = as.numeric(probed_tracker_epoch)) %>%
  group_by(ID, scene, probe, epoch, probed_tracker_epoch, tracker) %>%
  filter(probed_tracker_epoch == epoch) %>%
  summarise(hit = any(hit),
            td = mean(td),
            n = n()) %>%
  ungroup() %>%
  group_by(scene, epoch, probe, tracker) %>%
  summarise(hr = mean(hit),
            td = mean(td),
            n = n()) %>%
  ungroup()

ate_by_probe <- hr_by_probe %>%
  mutate(frame = probe) %>%
  left_join(exp_data, by = c("scene", "epoch", "frame", "tracker")) %>%
  group_by(scene) %>%
  mutate(ttwm_rank = rank(ttwm),
         hr.rank = rank(hr)) %>%
  ungroup()

```



## Sanity checks for scene level variation

```{r}

ate_by_probe %>%
  ggplot(aes(hr, fill = factor(scene))) +
  geom_histogram() +
  guides(color = FALSE)

cum_att <- inf_data %>%
  group_by(scene) %>%
  filter(frame == max(frame)) %>%
  summarize(final_catt = sum(cum_att)) %>%
  select(c(scene, final_catt)) %>%
  right_join(ate_by_probe, by = "scene") %>%
  mutate(final_catt = scale(final_catt))

cum_att %>%
  group_by(scene) %>%
  summarise(hr_mu = mean(hr),
            hr_sd = sd(hr),
            total_att = first(final_catt),
            p_is_target_mu = first(p_is_target_mu),
            ) %>%
  arrange(hr_mu) %>%
  ggplot(aes(y = hr_mu, x =reorder(scene, hr_mu))) +
  geom_point() +
  geom_errorbar(aes(ymin = hr_mu - hr_sd, ymax = hr_mu + hr_sd))
```

<!-- Looking at trial order -->

<!-- ```{r} -->
<!-- good_subjects_data %>% -->
<!--   filter(pbh) %>% -->
<!--   ggplot(aes(x = TrialOrder)) + -->
<!--   geom_bar() + -->
<!--   facet_grid(rows = vars(ID)) -->

<!-- good_subjects_data %>% -->
<!--   group_by(TrialOrder) %>% -->
<!--   summarise(probe_fp = mean(probe_fp), -->
<!--             d.prime = qnorm(mean(pbh) * 0.998 + 0.001) - qnorm(probe_fp*0.998 + 0.001)) %>% -->
<!--   ggplot(aes(x = TrialOrder, y = d.prime)) + -->
<!--   geom_col() -->

<!-- ``` -->


Focusing on specific scene

```{r}
spec_scene = 1:3

ate_by_probe %>%
  filter(scene %in% spec_scene) %>% 
  select(scene, epoch, tracker, hr, td, ttwm, zatt) %>%
  arrange(scene, epoch)

# good_subjects_data %>%
#   filter(scene %in% spec_scene) %>%
#   view()

timing_data <- good_subjects_data %>%
  ungroup() %>%
  filter(scene %in% spec_scene) %>%
  nest_by(ID) %>%
  mutate(idata = list(filter(inf_data, scene %in% spec_scene)),
         full = list(left_join(idata, data, by = c("scene", "frame")))) %>%
  select(-c(data, idata)) %>%
  unnest(cols = full) %>%
  select(scene, frame, tracker, ttwm, attention_mu, probe, ID, response_frame) %>%
  ungroup()

timing_data %>%
  ggplot(aes(x = frame)) +
  geom_line(aes(y = ttwm, color = factor(tracker))) +
  # geom_point(aes(y = attention_mu * 50, color = factor(tracker)),)+
  geom_vline(aes(xintercept = probe, color = "probe"), linetype = "dashed") + 
  geom_vline(aes(xintercept = probe + hit_window, color = "fp_cutoff"), linetype = "longdash") + 
  geom_vline(aes(xintercept = probe + probe_space, color = "trial_cutoff")) + 
  geom_histogram(aes(x =  response_frame), binwidth = 6) +
  facet_grid(rows = vars(scene))
```

```{r}

delay_by_probe <- good_subjects_data %>%
  # sorting out probed tracker
  pivot_longer(cols = starts_with("probe_"), 
               names_to = "probed_tracker_epoch",
               values_to = "tracker") %>%
  separate(probed_tracker_epoch, c(NA, NA, "probed_tracker_epoch")) %>%
  mutate(probed_tracker_epoch = as.numeric(probed_tracker_epoch)) %>%
  filter(probed_tracker_epoch == epoch, hit) %>%
  group_by(scene, probe, epoch, probed_tracker_epoch, tracker) %>%
  summarise(delay.mu = mean(delta_t),
            n = n(),
            delay.se = sd(delta_t) / sqrt(n)) %>%
  ungroup()

delay_ate_by_probe <- delay_by_probe %>%
  mutate(frame = probe) %>%
  left_join(exp_data, by = c("scene", "epoch", "frame", "tracker")) %>%
  group_by(scene) %>%
  mutate(ttwm_rank = rank(ttwm),
         delay.rank = rank(delay.mu),
         delay.conf_high = delay.mu + delay.se,
         delay.conf_low = delay.mu - delay.se) %>%
  ungroup()
```

```{r}
spec_scene = 1:3

delay_ate_by_probe %>%
  filter(scene %in% spec_scene) %>% 
  select(scene, frame, tracker, delay.mu, delay.se, ttwm, zatt) %>%
  arrange(scene, ttwm)

# good_subjects_data %>%
#   filter(scene %in% spec_scene) %>%
#   view()

subject_performance %>%
  filter(passed) %>%
  ggplot(aes(x = factor(ID), y = hr - fp)) +
  geom_col()
```



## Effect of weighted tracker centroid on hit rate


```{r}

ate_by_probe %>%
  ggplot(aes(x = ttwm, y = tttm)) +
  geom_point(aes(color = high_att))

ate_by_probe %>%
  ggplot(aes(x = tttm, y = hr)) +
  geom_point(aes(color = high_att))

ate_by_probe %>%
  ggplot(aes(x = tracker_to_dot_mean, y = hr)) +
  geom_point(aes(color = td))

ate_by_probe %>%
  ggplot(aes(x = attention_mu > 5.0, y = td)) +
  geom_violin()

ate_by_probe %>%
  ggplot(aes(x = ttwm, y = hr)) +
  geom_point(aes(color = td))


ate_by_probe %>%
  ggplot(aes(x = attention_mu, y = hr)) +
  geom_point(aes(color = td))

```

First take a look at just the tracker centroid mean

```{r}

wtm_fit <- ate_by_probe %>%
  with(lm_robust(hr ~ ttwm,))
wtm_fit %>%
  summary()

ttm_fit <- ate_by_probe %>%
  with(lm_robust(hr ~ tttm))
ttm_fit %>%
  summary()


```


### Res-res

```{r}

# for effect size + conf interval
ate_by_probe %>%
  with(lm(hr ~ zttwm + ztttm)) %>%
  summary()

# for variance explained

tttm_ttwm <- ate_by_probe %>%
  with(lm(zttwm ~ ztttm))
tttm_ttwm %>%
  summary()


ate_by_probe$pred_ttwm <- tttm_ttwm %>%
  predict(ate_by_probe)

tttm_hr <- ate_by_probe %>%
  with(lm(hr ~ ztttm))

tttm_hr %>%
  summary()


ate_by_probe$pred_hr <- tttm_hr %>%
  predict(ate_by_probe)

ate_by_probe <- ate_by_probe %>%
  mutate(res_ttwm = zttwm - pred_ttwm,
         res_hr = hr - pred_hr)


res_res_fit <- ate_by_probe %>%
  with(lm(res_hr ~ res_ttwm))
res_res_fit %>% 
  summary()

ate_by_probe$pred_res_hr <- res_res_fit %>%
  predict(ate_by_probe)
ate_by_probe <- ate_by_probe %>%
  mutate(res_res_hr = res_hr - pred_res_hr)

ate_by_probe %>%
  top_n(5, abs(res_res_hr))
ate_by_probe %>%
  top_n(-5, abs(res_res_hr))

ate_by_probe %>%
  ggplot(aes(x = res_ttwm, y = res_hr)) +
  geom_point() + 
  geom_smooth(method = "lm")

```
```{r}

# for variance explained

ttwm_tttm <- ate_by_probe %>%
  with(lm_robust(ztttm ~ zttwm,
                 # fixed_effects = ~ scene
                 ))
ttwm_tttm %>%
  summary()


ate_by_probe$pred_tttm <- ttwm_tttm %>%
  predict(ate_by_probe)

ttwm_hr <- ate_by_probe %>%
  with(lm_robust(hr ~ zttwm))

tttm_hr %>%
  summary()


ate_by_probe$pred_hr <- ttwm_hr %>%
  predict(ate_by_probe)

ate_by_probe <- ate_by_probe %>%
  mutate(res_tttm = ztttm - pred_tttm,
         res_hr = hr - pred_hr)


res_res_fit <- ate_by_probe %>%
  with(lm_robust(res_hr ~ res_tttm))
res_res_fit %>% 
  summary()

ate_by_probe %>%
  ggplot(aes(x = res_tttm, y = res_hr)) +
  geom_point(aes(color = high_att)) + 
  geom_smooth(method = "lm")
```

```{r}

# for effect size + conf interval
ate_by_probe %>%
  with(lm_robust(hr ~ zttwm + tracker_to_dot_mean )) %>%
  summary()

# for variance explained

tttm_ttwm <- ate_by_probe %>%
  with(lm_robust(zttwm ~ tracker_to_dot_mean,
                 # fixed_effects = ~ scene
                 ))
tttm_ttwm %>%
  summary()


ate_by_probe$pred_ttwm <- tttm_ttwm %>%
  predict(ate_by_probe)

tttm_hr <- ate_by_probe %>%
  with(lm_robust(hr ~ tracker_to_dot_mean))

tttm_hr %>%
  summary()


ate_by_probe$pred_hr <- tttm_hr %>%
  predict(ate_by_probe)

ate_by_probe <- ate_by_probe %>%
  mutate(res_ttwm = zttwm - pred_ttwm,
         res_hr = hr - pred_hr)


res_res_fit <- ate_by_probe %>%
  with(lm_robust(res_hr ~ res_ttwm))
res_res_fit %>% 
  summary()

ate_by_probe %>%
  ggplot(aes(x = res_ttwm, y = res_hr)) +
  geom_point(aes(color = tracker_to_dot_mean)) + 
  geom_smooth(method = "lm")


```
with fixed effects 

```{r}

# for effect size + conf interval
ate_by_probe %>%
  with(lm_robust(hr ~ zttwm + ztttm, fixed_effects =  ~ scene)) %>%
  summary()

# for variance explained

tttm_ttwm <- ate_by_probe %>%
  with(lm_robust(zttwm ~ ztttm, fixed_effects =  ~ scene))
tttm_ttwm %>%
  summary()


ate_by_probe$pred_ttwm <- tttm_ttwm %>%
  predict(ate_by_probe)

tttm_hr <- ate_by_probe %>%
  with(lm_robust(hr ~ ztttm, fixed_effects =  ~ scene))

tttm_hr %>%
  summary()


ate_by_probe$pred_hr <- tttm_hr %>%
  predict(ate_by_probe)

ate_by_probe <- ate_by_probe %>%
  mutate(res_ttwm = zttwm - pred_ttwm,
         res_hr = hr - pred_hr)


res_res_fit <- ate_by_probe %>%
  with(lm_robust(res_hr ~ res_ttwm))
res_res_fit %>% 
  summary()

ate_by_probe$pred_res_hr <- res_res_fit %>%
  predict(ate_by_probe)
ate_by_probe <- ate_by_probe %>%
  mutate(res_res_hr = res_hr - pred_res_hr)

ate_by_probe %>%
  top_n(5, abs(res_res_hr))
ate_by_probe %>%
  top_n(-5, abs(res_res_hr))

ate_by_probe %>%
  ggplot(aes(x = res_ttwm, y = res_hr)) +
  geom_point(aes(color = log_att_lead)) + 
  geom_smooth(method = "lm")

```
